Continous time Markov chain models; \\ extension, simulation and visualisation

### 2015-01-26 Response.tex

% 18
\item {
{\it
\textbf{
P57. The sentence `To determine the posterior odds, ... of that model' is vague.
}% END: textbf
}% END: it
}% END: item
\\
The sentence is rephrased:

\begin{quote}
\myeditsveighteen
\end{quote}

% 19
\item {
{\it
\textbf{
P85. Riemannian -> Riemann
}% END: textbf
}% END: it
}% END: item
\\
Corrected.

% 20
\item {
{\it
\textbf{
P86. The last sentence of Section 5.1.3 is not sufficiently clear. 
Please make clear why the use of mixed effects models could allow this.
}% END: textbf
}% END: it
}% END: item
\\
I changed the Subsection~\ref{sub:glm_epoch}, copied some bits from the hierarchical epoch model paper (under construction) and explained we mean the impact of various covariates as well as that by using MG94 parametrization we get a better resolution on selection parameters.

% 21
\item {
{\it
\textbf{
P88. It would be useful to receive a bit more detail what is meant by `infinite hidden Markov Model'.
}% END: textbf
}% END: it
}% END: item
\\
I introduce the definition of HMM's in a form of Remark, see Subsection~\ref{sub:dpp}.

### 2015-01-28 chapters/chapter01.tex

\cite{Baele2012} have proposed the first implementation of PS and SS into phylogenetic inference software.

Although offering tremendous improvements in bias and variance over the HME both PS and SS require considerable computational effort as the marginal likelihood can no longer be estimated from the likelihood trace that is being output from the standard MCMC analysis. 
% When only modest computation is invested to keep marginal likelihood manageable for large data sets, the estimates may suffer from considerable variance, preventing an accurate comparison of two models.
Further, great care must also be taken to specify proper priors for all parameters in Equation~\ref{eq:ss_ps}, so as to avoid numerical instabilities when the integration approaches the prior.

>>>>

\cite{Baele2012} have performed a comparative study on the performance of HME, the stabilized/smoothed HME (sHME), the AICM (a posterior simulation-based analogue of Akaike?s information criterion through Markov chain Monte Carlo, PS and SS in a phylogenetic framework.
The authors showed that PS and SS consistently outperformed the harmonic mean estimators as well as the AICM when comparing demographic models as well as relaxed clock models.
Although offering tremendous improvements in bias and variance over the HME both PS and SS require considerable computational effort as the (log) marginal likelihood can no longer be estimated from the likelihood trace that is being output from the standard MCMC analysis. 
Further, great care must also be taken to specify proper priors for all parameters in Equation~\ref{eq:ss_ps}, so as to avoid numerical instabilities when the integration approaches the prior \cite{Baele2013b}.
